### 2025-04-18 base-rates.qmd
20250418 - fixes

```{r}
rookiesDraftedEarly %>% 
  filter(position == "QB") %>%
  select(fantasyPoints) %>% 
  psych::describe()

rookiesDraftedEarly %>% 
  filter(position == "QB") %>%
  select(fantasyPoints) %>% 
  hist()
```

@@

rookiesDraftedEarly %>% 
  filter(position == "RB") %>%
  select(fantasyPoints) %>% 
  hist()

@@

@@

rookiesDraftedEarly %>% 
  filter(position == "WR") %>%
  select(fantasyPoints) %>% 
  hist()

@@

@@

rookiesDraftedEarly %>% 
  filter(position == "TE") %>%
  select(fantasyPoints) %>% 
  hist()

@@

>>>>

```{r}
rookiesDraftedEarly %>% 
  filter(position == "QB") %>%
  select(fantasyPoints) %>% 
  psych::describe()
```

```{r}
rookiesDraftedEarly %>% 
  filter(position == "QB") %>%
  select(fantasyPoints) %>% 
  hist()
```

@@

@@

```{r}
rookiesDraftedEarly %>% 
  filter(position == "RB") %>%
  select(fantasyPoints) %>% 
  hist()
```

@@

@@

```{r}
rookiesDraftedEarly %>% 
  filter(position == "WR") %>%
  select(fantasyPoints) %>% 
  hist()
```

@@

@@

```{r}
rookiesDraftedEarly %>% 
  filter(position == "TE") %>%
  select(fantasyPoints) %>% 
  hist()
```
